### 2013-05-09 doc/icml2013/evaluation.tex

As an example, one feature map we considered in the one-dimensional
setting $(b=1)$ was $x = (1, t, t^4, t^7)$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using Spectral Experts are shown in
\figureref{fig:curves}. We note that even on well-separated data such as
this, EM converged to the correct basin of attraction only 13\% of the time.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.png}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, n = 500,000$}
  \label{fig:hist}
\end{figure}

@@

\begin{table*}[tbhp]
\caption{Parameter error $\|\theta^* - \hat \theta\|_F$ ($n = 500,000$)
as the number of variables $b$, number of features $d$ and the number of components $k$ increases.
While Spectral by itself does not produce good parameter estimates, Spectral+EM improves
over EM significantly.
}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

One of the main reasons for the high variance is the variation across
random instances; some are easy for EM to find the global minima and
others more difficult. In general, while the spectral algorithm did not
recover parameters extremely well, it provided a good initialization for
EM.

To study the stability of the solutions returned by the spectral method,
consider the histogram in \figureref{fig:hist}, which shows the recovery
errors of the algorithms over 170 attempts on a dataset with $b = 1, d = 4,
k = 3$. Typically, the spectral algorithm returned a stable solution.
When these parameters were close enough to the true parameters, we found
that EM almost always converged to the global optima. Randomly
initialized EM only finds the true parameters a little over 10\% of the
time and shows considerably higher variance.

>>>>

As an example, one feature map we considered in the one-dimensional
setting $(b=1)$ was $x = (1, t, t^4, t^7)$. The data and the curves fit using
Spectral Experts, EM with random initialization and EM initialized with
the parameters recovered using Spectral Experts are shown in
\figureref{fig:curves}. We note that even on well-separated data such as
this, EM converged to the correct basin of attraction only 13\% of the time.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.png}
  \caption{Histogram over recovery errors between the three algorithms when $b = 1, d = 4, k = 3, n = 500,000$.}
  \label{fig:hist}
\end{figure}

@@

\begin{table*}[tbhp]
\caption{Parameter error $\|\theta^* - \hat \theta\|_F$ ($n = 500,000$)
as the number of base variables $b$, number of features $d$ and the number of components $k$ increases.
While Spectral by itself does not produce good parameter estimates, Spectral+EM improves
over EM significantly.
}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

One of the main reasons for the high variance is the variation across
random instances; some are easy for EM to find the global minima and
others more difficult. In general, while Spectral Experts did not
recover parameters by itself extremely well, it provided a good initialization for
EM.

To study the stability of the solutions returned by Spectral Experts,
consider the histogram in \figureref{fig:hist}, which shows the recovery
errors of the algorithms over 170 attempts on a dataset with $b = 1, d = 4,
k = 3$. Typically, Spectral Experts returned a stable solution.
When these parameters were close enough to the true parameters, we found
that EM almost always converged to the global optima. Randomly
initialized EM only finds the true parameters a little over 10\% of the
time and shows considerably higher variance.
